Output Summary

### 2021-08-31 03-post-process/output-plots.Rmd

plot_f = function(j) {
  par(yaxs = "r")
  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)), with(jags_data, carcs_spawned[,j]/carcs_sampled[,j])[observable], main = pops[j], ylim = c(0,1))
  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")

>>>>

plot_f = function(j) {
  par(yaxs = "r")
  plot_tseries(post_summ(post, sub_index("^phi_Sb_Sa[.+,pop]", pop = j)),
               get_obs_ests_multinomial(cbind(jags_data$carcs_spawned[,j], jags_data$carcs_sampled[,j] - jags_data$carcs_spawned[,j])[observable,], 1),
               main = pops[j], ylim = c(0,1))
  par(mar = c(1.5,1.5,2,0.5), yaxs = "i")
